openarchaeoCollaboration

### 2021-02-27 analysis/paper.Rmd
Keep GitHub data in main table

```{r data-github}
# Warning: slow
# TODO: map
gh_langs <- map(oarch$gh_repo, gh_lang)
gh_contribs <- map(oarch$gh_repo, gh_contrib)
gh_issues <- map(oarch$gh_repo, gh_issue)
gh_comments <- map(oarch$gh_repo, gh_comment)
gh_commits <- map(oarch$gh_repo, function(x) { print(x); gh_commit(x) })
```

>>>>

```{r data-github}
# Warning: slow
# TODO: map
oarch <- mutate(oarch,
                gh_langs = map(oarch$gh_repo, gh_lang),
                gh_contribs = map(oarch$gh_repo, gh_contrib),
                gh_issues = map(oarch$gh_repo, gh_issue),
                gh_comments = map(oarch$gh_repo, gh_comment),
                gh_commits = map(oarch$gh_repo, gh_commit),
)
```
